---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rozhlas

<!-- badges: start -->
[![R-CMD-check](https://github.com/skvrnami/rozhlas/workflows/R-CMD-check/badge.svg)](https://github.com/skvrnami/rozhlas/actions)
<!-- badges: end -->

The goal of `rozhlas` is to provide access to Czech Radio's open data API on broadcasting programme and Radio Wave's playlists.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("skvrnami/rozhlas")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r setup, warning=FALSE, message=FALSE}
library(dplyr)
library(rozhlas)
```

## Stations

Function `get_stations` returns data.frame with data on Czech Radio stations.
```{r}
stations <- get_stations()
glimpse(stations)
```

```{r}
stations %>% 
    select(id, name, type) %>%
    head() %>%
    knitr::kable()
```

## Programme

The data on Czech Radio's programme are available using four functions `get_current_programme` (for current day and all stations), `get_current_station_programme` (for current day and a specified station), `get_day_programme` (for a specified day and all stations) and `get_day_station_programme` (for a specified day and station).

```{r}
today_programme <- get_current_programme()
today_programme$plus %>%
    head() %>%
    knitr::kable()
```

```{r}
rz_today_programme <- get_current_station_programme("radiozurnal")
rz_today_programme %>%
    head() %>%
    knitr::kable()
```

```{r}
sept30 <- get_day_programme("2021-09-30")
sept30$plus %>%
    head() %>%
    knitr::kable()
```

```{r}
rz_sept30 <- get_day_station_programme("2021-09-30", "radiozurnal")
rz_sept30 %>%
    head() %>%
    knitr::kable()
```


## Playlists

The playlist are available only for the Radio Wave station by `get_wave_playlist` function for the current day and `get_day_wave_playlist` for a specific day.
```{r}
today_wave <- get_wave_playlist()
today_wave %>%
    head() %>% 
    knitr::kable()
```

```{r}
sept7_wave <- get_day_wave_playlist("2021-09-07")
sept7_wave %>%
    head() %>% 
    knitr::kable()
```

